\thetitle

### 2013-04-18 tfpie/tfpie.tex
fix secref

These constraints, while in detail specific to Northeastern and the
CCIS curriculum, are broadly similar to the requirements for the first
year at many universities.  Our course also attends to smaller and
more idiosyncratic elements of our curriculum, ranging from formal
reasoning to algorithmic analysis, as described in
section~\ref{sec:our-course}.

>>>>

These constraints, while in detail specific to Northeastern and the
CCIS curriculum, are broadly similar to the requirements for the first
year at many universities.  Our course also attends to smaller and
more idiosyncratic elements of our curriculum, ranging from formal
reasoning to algorithmic analysis, as described in the following
sections.
